Epidemiological Data Analysis

### 2023-10-03 analysis/epi_analysis.Rmd
revise prior pin plot

prior_pin_pl <- prior_pin %>%
  ggplot(aes(x = x, y = y)) +
  stat_lineribbon(point_interval = "mean_qi") +
  scale_fill_brewer() + 
  facet_wrap(~ virus) +
  labs(x = "s (delay in days)", y = expression(p[IN]*" (%)")) +
  scale_x_continuous(expand = c(0,0), breaks = seq(0, 10, 2)) +
  scale_y_continuous(expand = expansion(mult = c(0,0.05))) +
  theme_bw2() +
  theme(plot.title = element_text(hjust = 0), legend.position = "none")
prior_pin_pl

save_plot(prior_pin_pl, pdf_file = "../results/epi-data/incubation-periods.pdf", w = 16, h = 10)
```

>>>>

prior_pin_pl <- prior_pin %>%
  ggplot(aes(x = x, y = y)) +
  stat_lineribbon(point_interval = "mean_qi") +
  scale_fill_brewer() + 
  facet_wrap(~ virus, scales = "free_x") +
  labs(x = "s (delay in days)", y = expression(p[IN]*" (%)"), fill = "Prior distribution (CrI)") +
  scale_x_continuous(expand = c(0,0), breaks = seq(0, 10, 2)) +
  scale_y_continuous(expand = expansion(mult = c(0,0.05))) +
  theme_custom() +
  theme(plot.title = element_text(hjust = 0), legend.position = "top",
        panel.spacing = unit(25, units = "pt"), 
        plot.margin = margin(r = 10))
prior_pin_pl

save_plot(prior_pin_pl, pdf_file = "../results/epi-data/incubation-periods.pdf", w = 16, h = 11)
```
